Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 implementation.tex
Removed duplicate figure
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@914 ccdd05d5-56c1-461a-bf98-85f6876523b4

We have implemented a prototype of the low-latency filtering stage using an
open-source signal processing environment called \gstreamer\ \cite{gstreamer}.
\gstreamer\ is a vital component of many Linux systems, providing media
playback, authoring, and streaming on devices from cell phones to desktop
computers to streaming media servers.  Given the similarities of
gravitational- wave detector data to audio data it is not surprising that
\gstreamer\ is
useful for our purpose. \gstreamer\ also provides some useful stock signal
processing elements such as resamplers and filters.  We have extended the
\gstreamer\ framework by developing a library called \gstlal{}~\cite{gstlal}
that provides elements for gravitational-wave data-analysis.  Figure
\ref{fig:pipeline} describes schematically how we implement the \lloid\ algorithm
using \gstlal\ and \gstreamer\ components.
%
%
\begin{figure}[htbp]
	\includegraphics{figures/lloid-diagram.pdf}
	\caption{\label{fig:pipeline} Schematic of \lloid{} pipeline illustrating
signal flow.  Circles with arrows represent interpolation
\protect\includegraphics{figures/upsample-symbol.pdf} or decimation
\protect\includegraphics{figures/downsample-symbol.pdf}.  Circles with plus
signs represent summing junctions
\protect\includegraphics{figures/adder-symbol.pdf}.  Squares
\protect\includegraphics{figures/fir-symbol.pdf} stand for \fir{} filters.  Sample
rate decreases from the top of the diagram to the bottom.  In this diagram each
time slice contains three \fir\ filters that are linearly combined to produce
four output channels.  In a typical pipeline the number of \fir\ filters is
much less than the number of output channels.}
\end{figure}
The signal flow diagram drawn in figure \ref{fig:pipeline} contains several
distinct stages and parallel branches.  The stages are decimation, filtering
the data against the orthogonal templates, reconstruction of the original template basis, interpolation
and accumulation of the early-warning and final {\SNR}.  We outline the stages
below.

>>>>

We have implemented a prototype of the low-latency filtering stage using an
open-source signal processing environment called \gstreamer\ \cite{gstreamer}.
\gstreamer\ is a vital component of many Linux systems, providing media
playback, authoring, and streaming on devices from cell phones to desktop
computers to streaming media servers.  Given the similarities of
gravitational- wave detector data to audio data it is not surprising that
\gstreamer\ is
useful for our purpose. \gstreamer\ also provides some useful stock signal
processing elements such as resamplers and filters.  We have extended the
\gstreamer\ framework by developing a library called \gstlal{}~\cite{gstlal}
that provides elements for gravitational-wave data-analysis.  Figure
\ref{fig:pipeline} describes schematically how we implement the \lloid\ algorithm
using \gstlal\ and \gstreamer\ components.
